Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-02 Paper/results.tex
Fix typo and notes
added amr-wind timings still need nalu-wind timings

\subsubsection{Computational efficiency}
How much faster is AMR-Wind compared to Nalu-Wind?  \\
\fxnote{PUT SOME NUMBERS HERE FROM MIKE}

@@

The behavior of the TI and temperature profiles in figure
\ref{fig:CompareAMRallTTI} closely follows the shear and veer profiles
discussed above.  Despite all cases reaching a similar TI levels at
$z$=20m, the turbulence decays at different rates for each case until
reaching the top of the boundary layer.  The effect of the different
surface temperature changes is also visible in the horizontally
averaged temperature profiles.  Both the 10 m/s and 15 m/s impose
similar temperature changes (-1.4 K/hr and -1.5 K/hr, respectively)
and each similar temperatures at the ocean surface.  However, the
cooling effect in the very unstable 10 m/s case is limited to $z$<350
m, similar to the veer and turbulence profiles.

@@

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \centering
  \fxnote{Fix legend and line styles} \\
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{ \label{fig:AllStabilityRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$
    coefficient at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% All stability, turbulent L figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \centering
  \fxnote{Fix legend and marker styles} \\
  \includegraphics[width=3in]{figures/AllStability_Rij_LongitudinalLengthscale.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_LateralLengthscale.png}
  \caption{ \label{fig:AllStabilityLengthscale} Calculation of the
    averaged longitudinal and lateral lengthscale at $z$=20m for all
    ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsubsection{Computational efficiency}

For the 5 m/s SBL case AMR-Wind had a median time of 2.66 seconds per time step.
This means the entire simulation took about 6 hours to simulate 20k seconds 
of physical time. For this case a total of $288\times 288 \times 384$ cells were used 
which were solved in parallel using 972 MPI ranks. Simulations were carried out NREL's 
Eagle supercomputer and AMR-Wind was compiled using Intel 2018.
Typically on CPU's we see a strong scaling limit at around 15k cells per MPI rank. 
But for this case we used 32,768 cells per MPI rank which is about half the strong scaling limit.
The time per degree of freedom for AMR-Wind is
\[\frac{n_r t_{ts} }{n_{dofs}} = 8\times10^{-5}\]
where $n_r$ is the number of MPI ranks, $t_{ts}$ is time per time step, and $n_{dofs}$ is
the total number of degrees of freedom (for AMR-Wind we are using the number of cells).
This value allows us to compare speed relative to Nalu-Wind when using a different
grid and number of MPI ranks, where a smaller value means a faster time to solution.

In comparison the same case for Nalu-Wind takes x seconds per time step which
takes a total of x*4*20000/3600 hours to complete the simulation. This simulation was carried out 
on z MPI ranks on a grid that contains $400\times 400 \times 400$ cells. The equivalent
time per time step for Nalu-Wind is \fxnote{insert nalu-wind number here and x above}

@@

The behavior of the TI and temperature profiles in figure
\ref{fig:CompareAMRallTTI} closely follows the shear and veer profiles
discussed above.  Despite all cases reaching a similar TI levels at
$z$=20m, the turbulence decays at different rates for each case until
reaching the top of the boundary layer.  The effect of the different
surface temperature changes is also visible in the horizontally
averaged temperature profiles.  Both the 10 m/s and 15 m/s impose
similar temperature changes (-1.4 K/hr and -1.5 K/hr, respectively)
and each similar temperatures at the ocean surface.  However, the
cooling effect in the very stable 10 m/s case is limited to $z$<350
m, similar to the veer and turbulence profiles.

@@

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{ \label{fig:AllStabilityRij} Calculation of the averaged
    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$
    coefficient at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% All stability, turbulent L figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=3in]{figures/AllStability_Rij_LongitudinalLengthscale.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_LateralLengthscale.png}
  \caption{ \label{fig:AllStabilityLengthscale} Calculation of the
    averaged longitudinal and lateral lengthscale at $z$=20m for all
    ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
